THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-02-29 DishReflectometry/Paper1_v1.tex
moved system plot over to plots directory
got rid of eta and epsilon

\section{Antenna Reception With Multiple Reflections}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig. \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{microsys.pdf}
\caption{System}
\label{fig:sys}
\end{figure}

\noindent
Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
 \begin{equation}
a  =   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
   \label{eq:Sigma}
\end{equation}
Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).  We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $p_n(\hat{\theta})$, which is a function of angle on the sky.  Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle), denoted $\eta_f$.

@@

\begin{eqnarray}
\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n
\end{eqnarray}
Defining $s_{11}=\volt_{rec}/\volt_{trans}$ (the VNA measured quantity), this may be factored to yield
\begin{equation}
s_{11} = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\end{equation}
Adding in the zeroth term and rearranging, we have
\begin{equation}
s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\end{equation}
Comparing to Eq. \ref{eq:Sigma} and we find that
\begin{equation}
a = (1+\Gamma_d)\frac{\Gamma_f}{(1+\Gamma_{f})}\left(s_{11} + \frac{(1+\Gamma_f)^2}{\Gamma_f}- \Gamma_f\right)
\end{equation}
After rearranging and plugging in for $p_n(\hat{\theta})$ and $\eta_f$ we find
\begin{equation}
a = p_n(\hat{\theta})\left[\eta_f + \frac{\Gamma_f}{\eta_f}\left(s_{11} - \Gamma_f\right)\right]
\end{equation}
By measuring the feed separately, we may use that result for $\Gamma_f = s_{11,f}$ and $\eta_f = 1 + s_{11,f}$.

For power, we want the squared magnitude, or:
\begin{equation}
\raggedright
A(\hat{\theta}) = |aa^*|^2 =  P_n(\hat{\theta})\times ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\nonumber
\end{equation}
\begin{equation}
             \left[\epsilon_f +  2\operatorname{Re}\left(\frac{\Gamma_f}{\eta_f}(s_{11} - \Gamma_f)\right) 
                              + \frac{|\Gamma_f|^2}{\epsilon_{f}}|s_{11} - \Gamma_f|^2 \right]
\end{equation}
where $P_n(\hat{\theta})= |p_n(\hat{\theta})|^2$ is the normalized power pattern, and $\epsilon_f=|\eta_f|^2$ is the feed efficiency.

>>>>

\section{Antenna Reception With Multiple Reflections}
\label{sec:multiple}
To examine the performance of an antenna and feed in the presence of multiple reflections, think of the system as a screen at a distance $F$ from a feed (see Fig. \ref{fig:sys}), noting that this does ignore the sky pattern of the feed itself.  The screen reflects voltage as $\Gamma_d$ and transmits $(1+\Gamma_d)$ (see, {\em e.g.} Pozar).  Similarly, the feed reflects $\Gamma_f$ and transmits $(1+\Gamma_f)$.  The voltage pattern $\volt_{sky}$ is incident onto that system and  $(1+\Gamma_{d})(1+\Gamma_{f})$ is coupled into the cable leading from the feed. 
Additionally however, the voltage pattern is reflected off the feed ($\Gamma_f$), then the dish ($\Gamma_d$) and subsequently $(1+\Gamma_{f})$ of it reenters the feed with a roundtrip time delay $\Delta \tau=2F/c$. Hence, if $v_{sky}$ is reflected $n$ times in between the feed and the dish, the net voltage entering the feed after the
$n^{th}$ reflection may be written as:
\begin{eqnarray}
\volt_{rec} & = &  (1+\Gamma_d) (1+\Gamma_{f}) \volt_{sky}[1+ \Gamma_{f}\Gamma_{d} \dfngexp \nonumber \\
	&& + (\Gamma_{f}\Gamma_{d})^2  (\dfngexp)^{2}+ \nonumber \\
&&  ....+ (\Gamma_{f}\Gamma_{d})^{n} (\dfngexp)^{n}]
\end{eqnarray}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{plots/microsys.pdf}
\caption{System}
\label{fig:sys}
\end{figure}

\noindent
Defining $a=\volt_{rec}/\volt_{sky}$ and we see that 
 \begin{equation}
a  =   (1+\Gamma_d)(1+\Gamma_{f}) \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
   \label{eq:Sigma}
\end{equation}
Note that $n=0$ is when the initial wave enters the cable at the feed (where we assume we have set our reference plane).  We may identify $(1+\Gamma_d)$ as the voltage reception pattern of the antenna, denoted $p_n(\hat{\theta})$, which is a function of angle on the sky.  Additionally, $(1+\Gamma_f$) is the voltage efficiency for the feed (not a function of angle).

@@

\begin{eqnarray}
\volt_{rec} & = &  \Gamma_f \volt_{trans} \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp \Gamma_d\Gamma_f\dfngexp \nonumber \\
         && + \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^2 \nonumber \\
&&  ....+ \volt_{trans} (1+\Gamma_f)^2 \Gamma_{d} \dfngexp (\Gamma_d\Gamma_f\dfngexp)^n
\end{eqnarray}
Defining $s_{11}=\volt_{rec}/\volt_{trans}$ (the VNA measured quantity), this may be factored to yield
\begin{equation}
s_{11} = \Gamma_f + \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=1}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\end{equation}
Adding in the zeroth term and rearranging, we have
\begin{equation}
s_{11} +\frac{(1+\Gamma_f)^2}{\Gamma_f}-\Gamma_f = \frac{(1+\Gamma_f)^2}{\Gamma_{f}} \displaystyle\sum\limits_{n=0}^{N} [\Gamma_{f}\Gamma_{d}\dfngexp]^{n}
\end{equation}
Comparing to Eq. \ref{eq:Sigma} and we find that
\begin{equation}
a = (1+\Gamma_d)\frac{\Gamma_f}{(1+\Gamma_{f})}\left(s_{11} + \frac{(1+\Gamma_f)^2}{\Gamma_f}- \Gamma_f\right)
\end{equation}
After rearranging and plugging in for $p_n(\hat{\theta})$ we find
\begin{equation}
a = p_n(\hat{\theta})\left[(1+\Gamma_f) + \frac{\Gamma_f}{(1+\Gamma_f)}\left(s_{11} - \Gamma_f\right)\right]
\end{equation}
By measuring the feed separately, we may use that result for $\Gamma_f = s_{11,f}$.

For power, we want the squared magnitude, or:
\begin{equation}
\raggedright
A(\hat{\theta}) = |aa^*|^2 =  P_n(\hat{\theta})\times ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\nonumber
\end{equation}
\begin{equation}
             \left[|1+\Gamma_f|^2 +  2\operatorname{Re}\left(\frac{\Gamma_f}{(1+\Gamma_f)}(s_{11} - \Gamma_f)\right) 
                              + \frac{|\Gamma_f|^2}{|1+\Gamma_{f}|^2}|s_{11} - \Gamma_f|^2 \right]
\end{equation}
where $P_n(\hat{\theta})= |p_n(\hat{\theta})|^2$ is the normalized power pattern.  Note that $|1+\Gamma_f|^2$ is the feed efficiency ($\epsilon_f$).
